
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Van Cleef \& Arpels, Inc.}{USA - New York\\
\vspace{4mm}
Coordinator, High Jewelry\\Reference code USVCA - 00029613}
\date{June 28, 2014}
\opening{Dear Sir or Madam,}
\closing{Yours sincerely,}
% use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

Dear Mr. Kadakia,

I would like to express my interest in a position with Christie’s New York Jewelry team.  As the current Head of Catalogue Production/Cataloguer for Sotheby’s Jewelry department, in Geneva, I believe I would bring valuable professional experiences and skills to your department.

I have chosen to leave Switzerland and return to the United States in order to be closer to my family.   I would like to make this transition in early 2015 and am currently exploring job opportunities in New York City.

Why add me to your team?  I work hard, I love what I do, I learn quickly, and I would bring nearly four years of experience in handling, cataloguing, and selling some of the world’s most precious jewels.  In my current position, I am not only responsible for producing meticulously proofed and designed catalogues but also for preparing and supervising our public exhibitions.  This includes training and managing more than thirty temporary employees, deciding on the \textit{mis-en-sc\`{e}ne} of jewels within their showcases, selecting visuals, and managing client services including VIPs. Such experiences would prove valuable in my Coordinator work, especially in regard to the implementation of High Jewelry action plans, sales training, client treatment, and supporting the boutique network.
of jewels within their showcases, selecting visuals, and managing client services including VIPs.  I am also responsible for liaising between the Jewelry department and our Press and Marking departments and assisting with valuations when needed.  I believe these experiences would make me a valuable addition to your department.

My r\'{e}sum\'{e} further details my relevant qualifications. I have dual American and French citizenship and speak English, French and Italian. I would welcome the chance to discuss opportunities within your department. Thank you for your time and consideration.


\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}